### 2017-03-17 paper/modes.tex
pass on modes

Parallelism in test execution can be obtained at different levels.
Figure~\ref{fig:levels} illustrates relevant levels.  The highest
level indicates parallelism that can be obtained through different
machines on the network.  For examples, using virtual machines from a
cloud service.  The machine space sits under the ``network space'' and
provides \emph{low-level parallelism}.  In that case, computation can
be offloaded at different CPUs within a machine and at different
threads within each CPU.  Note that all these levels are
complementary.  For example, lower-level parallelization schemes could
leverage the computing power of server nodes in addition to the
aggregate processing power of the farm.

@@

This paper focuses at lower-level parallelism, which can be enabled
through build systems and testing frameworks.  Given the proliferation
of multi-core machines it is not surprising that testing frameworks
provide today support for parallel test execution (e.g.,
JUnit~\cite{junit-org}, TestNG~\cite{testng}, and NUnit~\cite{nunit}).
In the following we elaborate relevant features of testing frameworks
and builds systems.  We focused on Java, Maven, and JUnit but the
discussion can be generalized to other language and tools.

@@

@@

@@

\subsection{Build Systems}

Build systems delegate functionalities to the testing framework they
use~\cite{maven-surefire-plugin}.  Figure~\ref{fig:surefire}
illustrates how to configure Maven for mode
\ParClassSeqMeth{}~--~classes sequentially (default) and test methods
in parallel. Although this configuration is defined in the build file
(\eg, \emph{pom.xml} on Maven), these settings are forwarded to the
underlying testing framework (in this case, JUnit).

\subsubsection*{Forking JVMs}~
Build systems often rovide the option to \emph{fork} JVM instances
proportionally to available cores in the machine.  For Maven, the
options \CodeIn{forkCount} and \CodeIn{reuseForks} control this
feature~\cite{fork-and-parallel-execution-maven}.  Note that Maven
allocates each test class to exactly one JVM and there is no guarantee
to uniformly distribute load to each JVM given that the build system
uses classes as the unit to specify test tasks.  Consequently, only
combinations of fork with modes \Fix{??} are valid.

>>>>

Parallelism in test execution can be obtained at different levels.
Figure~\ref{fig:levels} illustrates relevant levels.  The highest
level indicates parallelism that can be obtained through different
machines on the network.  For instance, using virtual machines from a
cloud service to perform a distributed execution.  The machine space
sits under the ``network space'' and provides a \emph{lower-level}
parallelism.  In this case, computation can be offloaded at different
CPUs within a machine and at different threads within each CPU.  Note
that all these levels are complementary:  lower-level parallelization
schemes could leverage the computing power of server nodes in addition
to the aggregate processing power of the farm.

@@

This paper focuses at lower-level parallelism, which can be enabled
through build systems and testing frameworks.  Given the proliferation
of multi-core machines it is not surprising that testing frameworks
provide today support for parallel test execution (e.g.,
JUnit~\cite{junit-org}, TestNG~\cite{testng}, and NUnit~\cite{nunit}).
In the following we elaborate relevant features of build systems and
testing frameworks.  We focused on Java, Maven, and JUnit but the
discussion can be generalized to other language and tools.

@@

\subsection{Build Systems}
\label{sec:builder}

Several build systems support the execution of test suites in forked
processes running a Java virtual machine (JVM).  Each spawned process
runs an individual test suite and the builder outputs the aggregated
reports. When the testing framework finishes the execution, the forked
process can be reused for the next test suite in the queue. In this
level, the number of forked processes must be proportional to the
number of available CPUs otherwise, the high degree of concurrency
may affect the execution performance.  For instance, if the underlying
machine has four CPUs available, the builder could be configured to
spawn one process on each core to favor parallelism (in contrast to
several processes competing for a single core).

%%Build systems delegate functionalities to the testing framework they
%%use~\cite{maven-surefire-plugin}.  Figure~\ref{fig:surefire}
%%illustrates how to configure Maven for mode
%%\ParClassSeqMeth{}~--~classes sequentially (default) and test methods
%%in parallel. Although this configuration is defined in the build file
%%(\eg, \emph{pom.xml} on Maven), these settings are forwarded to the
%%underlying testing framework (in this case, JUnit).

@@

\subsubsection*{Example}~ \Fix{The list below shortly describes
the choices to control parallelism within a JVM.}

@@
